Parameter-less Population Pyramid

### 2014-01-15 Parameterless Population Pyramid/main.tex
abstract updated

\maketitle
\begin{abstract}
%Maximum 200 Words
  Real world applications of evolutionary techniques are often hindered by
  the need to determine problem specific parameter settings.
  While some previous methods have reduced or removed
  the need for parameter tuning, many do so
  by trading peak efficiency for general applicability.  The
  Parameter-less Population Pyramid (P3) is an evolutionary technique
  requiring \textbf{no} parameters which is still broadly applicable to
  many problem types. P3 strikes a balance between continuous
  integration of diversity with exploitative elitist operators,
  allowing it to solve easy problems quickly and hard problems
  eventually.  When compared with three state of the art optimization
  techniques across seven different problem classes, P3 always finds
  the optimum at least a constant factor \emph{\textbf{faster}} than
  the rest.  Even when optimally tuning comparison technique
  parameters, P3 has a lower evaluations to success growth complexity when test problems come
  from a random distribution.  Beyond empirical results, we suggest
  avenues for theoretical analysis of P3's expected runtime.  In
  general, while these are only the first results for P3, we feel they
  indicate wide applicability.
\end{abstract}

>>>>

\maketitle
\begin{abstract}
%Maximum 200 Words
  Real world applications of evolutionary techniques are often
  hindered by the need to determine problem specific parameter
  settings.  While some previous methods have reduced or removed the
  need for parameter tuning, many do so by trading efficiency for
  general applicability.  The Parameter-less Population Pyramid (P3)
  is an evolutionary technique that both requires \textbf{no}
  parameters and is broadly effective. P3 strikes a balance between
  continuous integration of diversity with exploitative elitist
  operators, allowing it to solve easy problems quickly and hard
  problems eventually.  When compared with three optimally tuned,
  state of the art optimization techniques, P3 always finds the
  optimum at least a constant factor \emph{\textbf{faster}} as shown
  on four benchmarks (Deceptive Trap, Deceptive Step Trap,
  Hierarchical If and only If, Rastrigin).  More importantly, on three
  randomized benchmarks (NK Landscapes, Ising Spin Glasses, MAX-SAT),
  P3 has a lower order of computational complexity as measured by
  evaluations.  Based on over 1 trillion evaluations, our results
  suggest P3 has wide applicatiblity to a broad class of real world
  problems.
\end{abstract}
